`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-16 inst/manuscript/manuscript.rmd
Paraphrasing to avoid doublication ("from") and clarifiy ("user" input);

From the identification of baseline and post-reduction fluorescense from 
fluorometer-generated spectra, via the calculation of the underlying statistics
and through publication-grade representation of the results, data analysis in 
the context of this assay has until now involved an extensive series of manual 
steps, at most supported by spreadsheet calculation facilities [see the 
supplementary material of @menon_opsin_2011 for extensive stepwise discussion]. Based on the
`R` free software environment for statistical computing and graphics [@r_core_team_r:_2015]
and prominently drawing on the power and elegance of the `ggplot2` plotting 
system [@wickham_ggplot2_2009], we here provide `flippant`, a comprehensive package
covering fast, reproducible data analysis and graphing for scramblase assays 
from raw fluorescense spectra with a simple parametrizing spreadsheet as the
sole required input.

>>>>

Starting with the identification of baseline and post-reduction fluorescense from 
fluorometer-generated spectra, via the calculation of the underlying statistics
and through publication-grade representation of the results, data analysis in 
the context of this assay has until now involved an extensive series of manual 
steps, at most supported by spreadsheet calculation facilities [see the 
supplementary material of @menon_opsin_2011 for extensive stepwise discussion]. Based on the
`R` free software environment for statistical computing and graphics [@r_core_team_r:_2015]
and prominently drawing on the power and elegance of the `ggplot2` plotting 
system [@wickham_ggplot2_2009], we here provide `flippant`, a comprehensive package
covering fast, reproducible data analysis and graphing for scramblase assays 
from raw fluorescense spectra with a simple parametrizing spreadsheet as the
sole required user input.
